**The Place of Interoception and Theory of Mind in Deception**

### 2021-11-11 scripts/claudia/data processing.Rmd

  select(ID, everything()) %>% #move ID column to front

@@

HCT <- read.csv("../heartbeat/HCT.csv", stringsAsFactors = FALSE)[-c(2,8:10)] %>% 
  rename(participant = Participant.number) %>%
  pivot_longer(!participant, names_to = "task", values_to = "hbcount_real")
data <- cbind(data, HCT)

>>>>

  select(ID, everything()) %>% # move ID column to front

@@

HCT <- read.csv("HCT_real.csv") %>% 
  pivot_longer(!task, names_to = "participant", values_to = "hbcount_real") %>%
  arrange(participant)
data <- cbind(data, HCT)
